

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{multicol}

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Thomas Wilding} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

\section{CONTACT}
\begin{minipage}{.5\textwidth}
tomwilding72@gmail.com \\
www.thomaswilding.com \\
0797-647-6687 \\
\end{minipage}% This must go next to `\end{minipage}`
\begin{minipage}{.5\textwidth}
\begin{flushright}
1 Chaucer Mansions \\
Queens Club Gardens \\
London \\
\end{flushright}
\end{minipage}

%----------------------------------------------------------------------------------------

\begin{resume}

\section{EDUCATION}

\textbf{MEng. in Computing}, with First Class Honours \\
Imperial College London, 2014. \\
Master’s Thesis: \textit{``Modelling and Prediction of Multiple Epidemic Phenomena''}

\textbf{Bachelor's in Computing}, with First Class Honours \\
Imperial College London, 2013. \\                                  

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{PROFESSIONAL EXPERIENCE}

\textbf{Accenture} - Analyst Software Engineer \hfill September 2014 - Current \\
Developed a reusable framework which enables rapid creation of integration services, using the latest Enterprise Integration technologies. \\
Key development role within an Agile team. We delivered APIs to a large telecommunications company through weekly code drops (Using the framework that we developed).
 
\textbf{Amadeus} - Intern Software Engineer \hfill April 2013 - September 2013 \\
Redesigned an existing application within the Departure Control System and gained experience of working in a Software Development company.

\textbf{DB Consulting} - Systems Developer \hfill June 2012 - September 2012 \\
Gained an initial insight into working as a software engineer, including functional testing within a team and taking certifications. \\


%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{COMPUTING \\ EXPERIENCE} 

\textbf{Java} \\
Wide range of experience implementing Java across multiple Enterprise systems. \\
\textbf{C} \\
Developed a basic OS alongside C programming courses. \\
\textbf{C++} \\
One of my favourite languages, I have programmed numerous C++ projects including graphical rendering systems and simulations. \\
\textbf{Haskell} \\
Implemented a Compiler and a series of functional programs in Haskell. \\
\textbf{SQL} \\
Studied relational algebra and SQL in various database modules. \\
\textbf{Web} \\
Created numerous web applications using the latest JavaScript frameworks, CSS and HTML. Awarded the IBM group project prize for a concurrent, real-time web application. Experience using Angular, Node, JQuery, Bootstrap and other web frameworks. \\
\textbf{Other} \\
Prolog, Perl, Scala, Android (Java), IOS (Swift and C\#), Unity (JS and C\#), MuleESB, Code management tools such as Git, Jenkins, CI. 

\newpage

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%---------------------------------------------------------------------------------------- 

\section{PROJECTS}

\textbf{Integration Framework} \\
Developed a reusable framework that enables rapid creation of standardised integration services. This project required full stack development and resulted in a extensible and reusable asset which significantly decreased costs and time to create integration services. The framework also ensures consistency and code quality across different implementations.

\textbf{Integration Delivery for a global Telecommunications Company} \\
Part of an agile team delivering APIs through weekly code drops, this was an aggressive delivery schedule that was only feasible through the use of our previously developed Integration Framework.

\textbf{Real-Time white-board} \\
I was awarded the IBM group project prize for my second year group project, called Scribboard, which is an application that enables multiple people to collaborate through drawing and other multimedia.

\textbf{Other Projects} \\
Many other projects in different computing domains such as Machine Learning, Robotics, Parallel Computing, Pervasive Computing, Parallel Algorithms, Simulation and Modelling, Graphics and Software Reliability.
%----------------------------------------------------------------------------------------
%	COMPUTING INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{PUBLICATIONS} 

\textbf{Uncertainty in On-The-Fly Epidemic Fitting}\\
Thomas Wilding, Roxana Danila, Marily Nika and William J. Knottenbelt. Computer Performance Engineering, Lecture Notes in Computer Science Volume 8721, 2014, p.135-148, Springer International Publishing. \\\\
\textbf{Going Multi-viral: Synthedemic Modelling of Internet-based Spreading Phenomena}\\
Thomas Wilding, Marily Nika, Dieter Fiems, Koen De Turck and William J. Knottenbelt. Valuetools, 8th International Conference on Performance Evaluation Methodologies and Tools, p.50-57 2015, ICST, appears in ACM.

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	COMPUTING INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{ADDITIONAL \\ SKILLS} 

Grade eight guitarist. \\
UK car driving license. \\
Interested in obtaining my Private Pilots License.\\

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}